 

### 2020-09-24 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

>>>>

Leaf traits vary along the vertical canopy profile following the pattern of light availability across the gradient [@poorterMetaanalysisPlantResponses2019b]. Leaves in the upper canopy that are exposed to more light differ in their traits compared to shaded leaves exposed to less light. Increasing number of studies point towards the importance of incorporating vertical canopy leaf trait variation in modelling for leaf economic spectrum (LES) [Chen et al. 2020], leaf thermoregular and thermal sensitivty which will provide a more accurate representation of within-canopy gradient response to increasing temperatures.[@fauset_differences_2018, @michaletzEnergeticCarbonEconomic2016, @niinemetsWorldwideAnalysisWithincanopy2015, Chen et al. 2020, REFS)
